\ttitle

### 2016-02-19 Chapters/CRP_Complications.tex
Post viva changes  - CRP Complications
- Legends, units to tables/figures
- Minor layout adjustments

%========================CRP vs POPF============================================
%CRP trends in a 2-panel figure and table showing p-values below it
\clearpage
\begin{figure}[t]
	\caption{Serum CRP levels in the first week after pancreaticoduodenectomy in patients with postoperative pancreatic fistula (POPF).}
	\label{fig:crp_comp_crp_popf}
	\centering
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_crp_popf_yes_no}
		\caption{POPF Absent vs. 
Any Grade}
		\label{fig:crp_comp_crp_popf_yes_no}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_crp_popf_isgps}
		\caption{POPF ISGPF Grades}
		\label{fig:crp_comp_crp_popf_isgps}
	\end{subfigure}
\end{figure}
\hfill
\input{Tables/crp_comp_vs_POPF_ISGPS_p_values_only}
%==============================================================================
\clearpage

\subsection{Postoperative CRP vs. infective complications}
The median CRP levels on or after postoperative day 3 were significantly higher in patients who developed clinically significant infective complications in the absence of a POPF (Fig. \ref{fig:crp_comp_infective_leak0}). 
Moreover, the median difference in CRP also increases from 56 mg/L on the third day to 79 mg/L on the seventh day. 
However, there was no such association in patients who developed a POPF (Fig. \ref{fig:crp_comp_infective_leak1}).

@@

%========================CRP vs Infections====================================
%CRP trends vs infections in patients with or without popf in a 2-panel figure and table showing median, iqr and p-values below it
\clearpage
\begin{figure}[t]
	\caption{Relationship between postoperative CRP and clinically significant infective complications in patients without (A) and with (B) POPF.}
	\label{fig:crp_comp_infective_leak}
	\centering
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_infective_leak0}
		\caption{Patients with \textbf{\underline{no}} POPF}
		\label{fig:crp_comp_infective_leak0}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_infective_leak1}
		\caption{Patients with POPF}
		\label{fig:crp_comp_infective_leak1}
	\end{subfigure}
\end{figure}
\vfill
\input{Tables/crp_comp_vs_infections_popf_y1n0}
%==============================================================================
\clearpage

@@

%========================ROC Curves==========================================
\clearpage
\begin{figure}[t]
	\caption{Receiver operating characteristics analysis of C-reactive protein as a marker of postoperative infective complications.}
	\label{fig:crp_comp_ROC_infection}

	\centering
	\begin{subfigure}{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_ROC_infection_D3}
		\caption{Day 3}
		\label{fig:crp_comp_ROC_infection_D3}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_ROC_infection_D4}
		\caption{Day 4}
		\label{fig:crp_comp_ROC_infection_D4}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_ROC_infection_D5}
		\caption{Day 5}
		\label{fig:crp_comp_ROC_infection_D5}
	\end{subfigure}
	\begin{subfigure}{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_ROC_infection_D6}
		\caption{Day 6}		
		\label{fig:crp_comp_ROC_infection_D6}
	\end{subfigure}
	\begin{subfigure}{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_ROC_infection_D7}
		\caption{Day 7}
		\label{fig:crp_comp_ROC_infection_D7}
	\end{subfigure}
\end{figure}
\vfill
\input{Tables/crp_comp_ROC_infections_noPOPF}
%=============================================================================

>>>>

\subsection{Postoperative CRP vs. infective complications}
The median CRP levels on or after postoperative day 3 were significantly higher in patients who developed clinically significant infective complications in the absence of a POPF (Fig. \ref{fig:crp_comp_infective_leak0}). 
%Moreover, the median difference in CRP also increases from 56 mg/L on the third day to 79 mg/L on the seventh day. 
However, there was no such association between CRP and infective complications in patients who developed a POPF (Fig. \ref{fig:crp_comp_infective_leak1}).

@@

\clearpage
%========================CRP vs POPF============================================
%CRP trends in a 2-panel figure and table showing p-values below it
\begin{figure}[t]
	\centering
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_crp_popf_yes_no}
		\caption{POPF Absent vs. 
			Any Grade}
		\label{fig:crp_comp_crp_popf_yes_no}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_crp_popf_isgps}
		\caption{POPF ISGPF Grades}
		\label{fig:crp_comp_crp_popf_isgps}
	\end{subfigure}
	\caption[Serum CRP levels in the first week after pancreaticoduodenectomy in patients with postoperative pancreatic fistula.]
	{Serum CRP levels in the first week after pancreaticoduodenectomy in patients with postoperative pancreatic fistula (POPF).
		\\ Median daily CRP levels in the first postoperative week in 188 patients undergoing pancreaticoduodenectomy were compared between patients who developed a postoperative pancreatic fistula (POPF) and those who did not develop a POPF. Figure A shows a significantly raised CRP in the presence of a pancreatic fistula. However, severity of POPF did not affect CRP levels in the first postoperative week as shown in Figure B. Error bars represent 95\% confidence interval for the median.
	}
	\label{fig:crp_comp_crp_popf}
\end{figure}
%\hfill
\input{Tables/crp_comp_vs_POPF_ISGPS_p_values_only}
%==============================================================================
\clearpage

%========================CRP vs Infections====================================
%CRP trends vs infections in patients with or without popf in a 2-panel figure and table showing median, iqr and p-values below it
\begin{figure}[t]
	\label{fig:crp_comp_infective_leak}
	\centering
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_infective_leak0}
		\caption{Patients with \textbf{\underline{no}} POPF}
		\label{fig:crp_comp_infective_leak0}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_infective_leak1}
		\caption{Patients with POPF}
		\label{fig:crp_comp_infective_leak1}
	\end{subfigure}
	\caption[Relationship between postoperative CRP and clinically significant infective complications in patients without (A) and with (B) POPF.]
	{Relationship between postoperative CRP and clinically significant infective complications in patients without (A) and with (B) POPF.
		\\Median CRP was significantly higher in patients who developed infective complications in the absence of a pancreatic fistula (A). However, this difference was not seen in the presence of a pancreatic fistula (B). Error bars represent 95\% confidence interval for the median.
	}
\end{figure}

\input{Tables/crp_comp_vs_infections_popf_y1n0}
%==============================================================================
\clearpage

@@

%========================ROC Curves==========================================
\clearpage
\begin{figure}[t]
	\centering
	\begin{subfigure}{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_ROC_infection_D3}
		\caption{Day 3}
		\label{fig:crp_comp_ROC_infection_D3}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_ROC_infection_D4}
		\caption{Day 4}
		\label{fig:crp_comp_ROC_infection_D4}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_ROC_infection_D5}
		\caption{Day 5}
		\label{fig:crp_comp_ROC_infection_D5}
	\end{subfigure}
	\begin{subfigure}{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_ROC_infection_D6}
		\caption{Day 6}		
		\label{fig:crp_comp_ROC_infection_D6}
	\end{subfigure}
	\begin{subfigure}{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/crp_comp_ROC_infection_D7}
		\caption{Day 7}
		\label{fig:crp_comp_ROC_infection_D7}
	\end{subfigure}
	\caption[Receiver operating characteristics analysis of C-reactive protein as a marker of postoperative infective complications.]
	{Receiver operating characteristics analysis of C-reactive protein as a marker of postoperative infective complications.
		\\In the 126 patients who did not develop a postoperative pancreatic fistula, C-reactive protein levels as early as the third and fourth postoperative days had a high negative predictive value of 0.79 (for Day 3  CRP $\leq$ 178 mg/l) and 0.83 (for Day 4 CRP $\leq$125 mg/l ) respectively for the prediction of infective complications.}
	\label{fig:crp_comp_ROC_infection}
\end{figure}
\vfill
\input{Tables/crp_comp_ROC_infections_noPOPF}
%=============================================================================
